<span style="color:red;">How to build a house with<br />Advanced Normalization Tools (*ANTs*)</span>

### 2014-09-03 ants2015build.Rmd
WIP: regular update

<div align="center"><img src="./logo.png" frameborder="0"></img></div>

@@

@@

@@

## ANTs & Neuroscience

We need statistical image analysis <br />at several scales in modern neuroscience

* Macro: *in vivo* structural and functional MRI

* Micro:  high-resolution post-mortem MRI links with in vivo MRI

* Nano: neuron reconstruction ...

* Solutions that are consistent across these scales have the potential
to build multi-scale feature sets or templates and provide new
insights into brain structure and function

* E.g. Parcellation constraints based on histology, tractography, function ...

* Statistical definitions of anatomy/pathology?

* Reinvention of these solutions within each lab ... can we mitigate this?

* Reduce, reuse, recycle ...

## Financial impact

* The **high error rate** in software makes testing for quality assurance critically important.

* Bugs exist **Everywhere**: so don't freak out if we admit we have bugs:  we're just being honest ( and not all devs are )

* Virtually every business in the United States now depends on software for development, production, distribution, and after-sales support of products and services.

* A 2002 NIST study estimated the direct costs to the software supply chain due to failure to identify (**successfully test for**) "bugs"

* We are better at this than most ... **not perfect**

* The estimate of direct costs compiled from industry survey data for the U.S. economy was **\$60 billion per year**

* ... this estimate did not include costs to end users such as lost business (for example, the cost of shutting down the New York Mercantile Exchange in 1998 due to a software failure).

## ANTs: Saving society \$\$\$

starting with neuroscience ...

@@

```
    An algorithm must use prior knowledge about a problem 
    to do well on that problem 
```

## Words of warning

@@

## Words of warning

@@

>>>>

<div align="center"><img src="./figures/brian_and_edie_sedgwick.jpg" frameborder="0"></img></div>

@@

BBA & NT

@@

![](./figures/lion.png)

@@

... to correct a misconception about diffeomorphisms ...

@@

```
    An algorithm must use prior knowledge about a problem 
    to do well on that problem

```

## On documentation

@@

## On documentation

@@

## On documentation

![](figures/blindmen.jpg)
